---
title: "Disaster Survey Sheet"
output:
  html_document:
    toc: true
    toc_depth: 3
  pdf_document:
    pandoc_args: --latex-engine=xelatex
---


```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(lubridate)
library(jsonlite)
library(knitr)
library(ggplot2)
library(leaflet)
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
options (scipen=4)
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#999999", "#000000", "#8856a7")

#`r disastername`, 
```

*Report Date: `r Sys.Date()`*

### Property Information

Name: 

Address:

Municipality:

Zip Code:

County:

Phone:

Type of Applicant or Structure:

Homeowner or Renter:

#### Insurance Infomration

Insurance Agent Name:

Insurance Agent Phone:

Flood Insurance:

### Estimated Disaster Loss Details

```{r loss_table, echo=FALSE, warning=FALSE, message=FALSE}
# row for each of structure, contents, land and improvements
# bring in variables for market value, amount damaged by disaster, amount covered by insurance
structure <- c("Structure", marketvalue_structure, disaster_structure, insurance_structure)
contents <- c("Contents", marketvalue_contents, disaster_contents, insurance_contents)
landimprov <- c("Land & Improvements", marketvalue_land, disaster_land, insurance_land)

# bind these
loss_table <- rbind(structure, contents, landimprov)
colnames(loss_table) <- c("Area", "MarketValue", "DisasterLoss", "InsuranceCovered")

# calculate amount and percent of uninsured loss
loss_table$UninsuredLoss <- loss_table$DisasterLoss - loss_table$InsuranceCovered
loss_table$UninsuredLossPercent <- loss_table$UninsuredLoss / loss_table$MarketValue

kable(loss_table, col.names = c("Market Value", "Disaster Loss", "Covered by Insurance",
                                "Uninsured Loss", "Uninsured Loss Percentage"))

```


### Building Damage

Damage Category: 

```{r damage_bysystem, echo=FALSE, warning=FALSE, message=FALSE}
foundation <- c("Foundation", damage_foundation)
floor <- c("Floor", damage_floor)
exterior <- c("Exterior Walls", damage_exterior)
roof <- c("Roof", damage_roof)
interior <- c("Interior Walls", damage_interior)
plumbing <- c("Plumbing", damage_plumbing)
heat_ac <- c("Heating / AC", damage_hvac)
electrical <- c("Electrical", damage_electrical)

systemdamage <- rbind(foundation, floor, exterior, roof, interior, plumbing, heat_ac, electrical)
colnames(systemdamage) <- c("SystemArea", "PercentDamange")
kable(systemdamage, col.names = c("System Area", "Percent Damaged"))

# thoughts on section of report
# Estimated Replacement Cost looks like sum of percent damanged times fair market value of property
# which is loss_table$MarketValue

```


Total % Damanged:`r round(sum(systemdamage$PercentDamange),0)`%

Estimated Replacement Cost: `r (sum(systemdamage$PercentDamange * sum(loss_table$MarketValue))`

Estimated Damage to Contents: `r sum(loss_table$DisasterLoss[loss_table$Area=="Contents"])`

Total Estimated Damange = `r (sum(systemdamage$PercentDamange * sum(loss_table$MarketValue)) + sum(loss_table$DisasterLoss[loss_table$Area=="Contents"])`

### Comments


### Assessor

Name of Assessor:

Date:


```{r map}
# map.data <- filter(muni.data, !is.na(Violation), !is.na(lat))
# leaflet() %>%
#       # use the CartoDB map for more subdued map tile colors
#       addProviderTiles("CartoDB.Positron") %>%
#       setView(lng = -79.8, lat = 40.4212, zoom = 12) %>%
#       addCircleMarkers(data = map.data,
#                        lng = ~long, lat = ~lat, 
#                        popup = paste("Violation:", map.data$Violation,
#                                      "<br> Initial Date:", map.data$EventDate),
#                  # the marker clusters gives us a nice visual 
#                  # effect where when we zoom out points cluster
#                  # together, and as we zoom in they are pulled apart
#                  # showing the individual markers.
#                  #clusterOptions = markerClusterOptions()
#                  radius = 5,
#                  stroke = TRUE,
#                  color = "#323232",
#                  weight = 3,
#                  fillColor = "#7fcdbb",
#                  fillOpacity = 0.7
#                  ) 
```

