---
title: "Disaster Survey Sheet"
output:
  html_document:
    toc: true
    toc_depth: 3
  pdf_document:
    pandoc_args: --latex-engine=xelatex
---


```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(lubridate)
library(jsonlite)
library(knitr)
library(ggplot2)
library(leaflet)
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
options (scipen=4)
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#999999", "#000000", "#8856a7")

###### FOR TESTING #####
field_data <- read.csv("MOCK_DATA.csv", header=TRUE, sep=",")
report_id = 27
#`r disastername`, 
```

*Report Date: `r Sys.Date()`*

### Property Information

Name: `r field_data$name_property_owner[id=report_id]`

Address: `r field_data$street_address[id=report_id]`

Municipality: `r field_data$city[id=report_id]`

Zip Code: `r field_data$zip_code[id=report_id]`

County: `r field_data$county[id=report_id]`

Phone: `r field_data$phone_number[id=report_id]`

Type of Applicant or Structure: `r field_data$property_type[id=report_id]`

Homeowner or Renter: `r field_data$owner_type[id=report_id]`

#### Insurance Information

Insurance Agent Name: `r field_data$name_insurance[id=report_id]`

Insurance Agent Phone: `r field_data$phone_insurance[id=report_id]`

Flood Insurance: `r field_data$flood_insurance[id=report_id]`

### Estimated Disaster Loss Details

```{r loss_table, echo=FALSE, warning=FALSE, message=FALSE}
# row for each of structure, contents, land and improvements
# bring in variables for market value, amount damaged by disaster, amount covered by insurance
structure <- data.frame("Structure", field_data$marketvalue_structure[id=report_id],
               field_data$disaster_structure[id=report_id], 
               field_data$insurance_structure[id=report_id])
colnames(structure) <- c("Area", "MarketValue", "DisasterLoss", "InsuranceCovered")
contents <- data.frame("Contents", field_data$marketvalue_contents[id=report_id], 
              field_data$disaster_contents[id=report_id], 
              field_data$insurance_contents[id=report_id])
colnames(contents) <- c("Area", "MarketValue", "DisasterLoss", "InsuranceCovered")
landimprov <- data.frame("Land & Improvements", field_data$marketvalue_land[id=report_id], 
                field_data$disaster_land[id=report_id], 
                field_data$insurance_land[id=report_id])
colnames(landimprov) <- c("Area", "MarketValue", "DisasterLoss", "InsuranceCovered")

# bind these
loss_table <- rbind(structure, contents, landimprov)

# calculate amount and percent of uninsured loss
loss_table$UninsuredLoss <- loss_table$DisasterLoss - loss_table$InsuranceCovered
loss_table$UninsuredLossPercent <- loss_table$UninsuredLoss / loss_table$MarketValue

kable(loss_table, col.names = c("Area", "Market Value", "Disaster Loss", "Covered by Insurance",
                                "Uninsured Loss", "Uninsured Loss Percentage"),
      row.names = F)

```


### Building Damage

Damage Category: **`r field_data$damage_category[id=report_id]`**

```{r damage_bysystem, echo=FALSE, warning=FALSE, message=FALSE}
foundation <- data.frame("Foundation", field_data$damage_foundation[id=report_id])
colnames(foundation) <- c("Area", "PercentDamange")
floor <- data.frame("Floor", field_data$damage_floor[id=report_id])
colnames(floor) <- c("Area", "PercentDamange")
exterior <- data.frame("Exterior Walls", field_data$damage_exterior[id=report_id])
colnames(exterior) <- c("Area", "PercentDamange")
roof <- data.frame("Roof", field_data$damage_roof[id=report_id])
colnames(roof) <- c("Area", "PercentDamange")
interior <- data.frame("Interior Walls", field_data$damage_interior[id=report_id])
colnames(interior) <- c("Area", "PercentDamange")
plumbing <- data.frame("Plumbing", field_data$damage_plumbing[id=report_id])
colnames(plumbing) <- c("Area", "PercentDamange")
heat_ac <- data.frame("Heating / AC", field_data$damage_hvac[id=report_id])
colnames(heat_ac) <- c("Area", "PercentDamange")
electrical <- data.frame("Electrical", field_data$damage_electrical[id=report_id])
colnames(electrical) <- c("Area", "PercentDamange")

systemdamage <- rbind(foundation, floor, exterior, roof, interior, plumbing, heat_ac, electrical)
colnames(systemdamage) <- c("SystemArea", "PercentDamange")
kable(systemdamage, col.names = c("System Area", "Percent Damaged"), row.names=F)


# thoughts on section of report
# Estimated Replacement Cost looks like sum of percent damanged times fair market value of property
# which is loss_table$MarketValue

```


Total % Damaged: `r round(sum(systemdamage$PercentDamange)*100,0)`%

Estimated Replacement Cost: $ `r (sum(systemdamage$PercentDamange * sum(loss_table$MarketValue)))`

Estimated Damage to Contents: $ `r sum(loss_table$DisasterLoss[loss_table$Area=="Contents"])`

Total Estimated Damange = $ `r (sum(systemdamage$PercentDamange * sum(loss_table$MarketValue)) + sum(loss_table$DisasterLoss[loss_table$Area=="Contents"]))`

### Comments

`r field_data$comments[id=report_id]`

### Assessor

Name of Assessor: `r field_data$name_of_assessor[id=report_id]`

Date: `r field_data$date[id=report_id]`


```{r map}
# map.data <- filter(muni.data, !is.na(Violation), !is.na(lat))
# leaflet() %>%
#       # use the CartoDB map for more subdued map tile colors
#       addProviderTiles("CartoDB.Positron") %>%
#       setView(lng = -79.8, lat = 40.4212, zoom = 12) %>%
#       addCircleMarkers(data = map.data,
#                        lng = ~long, lat = ~lat, 
#                        popup = paste("Violation:", map.data$Violation,
#                                      "<br> Initial Date:", map.data$EventDate),
#                  # the marker clusters gives us a nice visual 
#                  # effect where when we zoom out points cluster
#                  # together, and as we zoom in they are pulled apart
#                  # showing the individual markers.
#                  #clusterOptions = markerClusterOptions()
#                  radius = 5,
#                  stroke = TRUE,
#                  color = "#323232",
#                  weight = 3,
#                  fillColor = "#7fcdbb",
#                  fillOpacity = 0.7
#                  ) 
```

